QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.1.tex
consistent formatting of NP

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Quadratic Programming in a nutshell}\label{sec:QPbasic}

@@

\textcolor{red}{In the rest of this paper, we shall sometimes refer to {\it exact solutions} of quadratic programs. In view of the fact that their solutions may be irrational, this notation deserves a comment. If the decision version of the problem being referred to is in NP (e.g.~LP, MILP, QP \cite{vavasis90a}), then the assumption is that all rational numbers can be represented exactly by a Turing Machine (TM). 
%This assumption has the same limitation as the assumption that TMs defined on integers are a faithful abstraction of a real computer, namely that the range of integers needing a representation is bounded. 
If there is no known proof that the problem being solved (or its decision version) is in NP, then there are four main approaches:
\begin{enumerate}
\item finding a representable solution $x'$ such that $\|x'-x^\ast\|_\infty\le\varepsilon$, where $x^\ast$ is the true solution, $\varepsilon>0$ is given, and representable means having a polynomially sized description length
% ``
(in function of the instance size) \cite{hochbaum2};
\item using the {\it Thom encoding} of an algebraic number \cite[Prop.~2.28]{pollack} (limited to problems involving polynomials);
\item using the optimality gap: finding a representable solution $x'$ such that $|f(x')-f(x^\ast)|\le\varepsilon$, where $f$ is the objective function, $x^\ast$ is the true solution, $\varepsilon>0$ is given
%, and representable is as above 
(limited to optimization problems);\label{optgap}
\item using a computational model according to which every elementary computation on the reals takes $O(1)$ and returns an exact result \cite[p.~24]{blum}.
\end{enumerate}
Approach \ref{optgap} in the list above is the one most often used in computational papers, including the present one.}

>>>>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\section{Quadratic Programming in a Nutshell}\label{sec:QPbasic}

@@

\textcolor{red}{In the rest of this paper, we shall sometimes refer to {\it exact solutions} of quadratic programs. In view of the fact that their solutions may be irrational, this notation deserves a comment. If the decision version of the problem being referred to is in $\mathcal{NP}$ (e.g.~LP, MILP, QP \cite{vavasis90a}), then the assumption is that all rational numbers can be represented exactly by a Turing Machine (TM). 
%This assumption has the same limitation as the assumption that TMs defined on integers are a faithful abstraction of a real computer, namely that the range of integers needing a representation is bounded. 
If there is no known proof that the problem being solved (or its decision version) is in $\mathcal{NP}$, then there are four main approaches:
\begin{enumerate}
\item finding a representable solution $x'$ such that $\|x'-x^\ast\|_\infty\le\varepsilon$, where $x^\ast$ is the true solution, $\varepsilon>0$ is given, and representable means having a polynomially sized description length
% ``
(in function of the instance size) \cite{hochbaum2};
\item using the {\it Thom encoding} of an algebraic number \cite[Prop.~2.28]{pollack} (limited to problems involving polynomials);
\item using the optimality gap: finding a representable solution $x'$ such that $|f(x')-f(x^\ast)|\le\varepsilon$, where $f$ is the objective function, $x^\ast$ is the true solution, $\varepsilon>0$ is given
%, and representable is as above 
(limited to optimization problems);\label{optgap}
\item using a computational model according to which every elementary computation on the reals takes $O(1)$ and returns an exact result \cite[p.~24]{blum}.
\end{enumerate}
Approach \ref{optgap} in the list above is the one most often used in computational papers, including the present one.}

### 2018-02-08 methods.tex
consistent formatting of NP

\subsubsection{Incomplete methods}

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Asymptotically complete methods}\label{sss:asymc}

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Complete methods}\label{s:complete}

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This term has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. For example, te decision version of \textit{QCL} is known to be in the complexity class \textbf{NP} \cite{vavasis90a}, whereas the same is not known about \textit{LCQ}, even with zero objective. On the other hand, there exists a method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of \textit{LCQ} with zero objective function.

>>>>

\subsubsection{Incomplete Methods}

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Asymptotically Complete Methods}\label{sss:asymc}

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Complete Methods}\label{s:complete}

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This term has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. For example, the decision version of \textit{QCL} is known to be in the complexity class $\mathcal{NP}$ \cite{vavasis90a}, whereas the same is not known about \textit{LCQ}, even with zero objective. On the other hand, there exists a method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of \textit{LCQ} with zero objective function.
